Distinction Centrality Analysis

### 2025-07-20 analysis.qmd
new wheel who dis

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   library(patchwork)
   source(here("Functions", "distinction.R"))
   source(here("Functions", "make.broker.trees.R"))
   source(here("Functions", "make.broker.cliques.R"))
   source(here("Functions", "plot.graph.norm.R"))
   source(here("Functions", "tab.cent.R"))
```

@@

```{r Toy Examples}
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- g5 + edge(6,1) # circle graph plus triangle
   g7 <- g5 + edge(7,4) # circle graph plus long tie
   g8 <- make_full_graph(7, directed = FALSE) # clique
   g9 <- make_full_graph(6, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(1,7) # kite
   g10 <- union(make_ring(7), make_star(7, center = 1, mode = "undirected"))
   g10 <- g10 + edge(2,7)
```

```{r Toy Networks Plots}
   png(here("Plots", "Toys", "star.png"))
   plot.graph.norm(g1, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "sf.png"))
   plot.graph.norm(g2, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "intra.png"))
   plot.graph.norm(g3, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "inter.png"))
   plot.graph.norm(g4, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "circle.png"))
   plot.graph.norm(g5, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-triangle.png"))
   plot.graph.norm(g6, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-long.png"))
   plot.graph.norm(g7, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "clique.png"))
   plot.graph.norm(g8, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "kite.png"))
   plot.graph.norm(g9, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "wheel.png"))
   plot.graph.norm(g10, l = "kk")
   dev.off()
```

>>>>

```{r Loading Functions}
   library(igraph)
   library(ggraph)
   library(here)
   library(networkdata)
   library(ggpubr)
   library(patchwork)
   library(dplyr)
   source(here("Functions", "distinction.R"))
   source(here("Functions", "make.broker.trees.R"))
   source(here("Functions", "make.broker.cliques.R"))
   source(here("Functions", "plot.graph.norm.R"))
   source(here("Functions", "tab.cent.R"))
```

@@

```{r Toy Examples}
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- g5 + edge(6,1) # circle graph plus triangle
   g7 <- g5 + edge(7,4) # circle graph plus long tie
   g8 <- make_full_graph(7, directed = FALSE) # clique
   g9 <- make_full_graph(6, directed = FALSE)
   g9 <- add_vertices(g9, 1)
   g9 <- g9 + edge(1,7) # kite
   g10 <- g1 + edge(2,3)
   g10 <- g10 + edge(3,4)
   g10 <- g10 + edge(4,5)
   g10 <- g10 + edge(5,6)
   g10 <- g10 + edge(6,7)
   g10 <- g10 + edge(7,2) #wheel graph
```

```{r Toy Networks Plots}
   source(here("Functions", "plot.graph.norm.R"))
   png(here("Plots", "Toys", "star.png"))
   plot.graph.norm(g1, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "sf.png"))
   plot.graph.norm(g2, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "intra.png"))
   plot.graph.norm(g3, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "inter.png"))
   plot.graph.norm(g4, l = "auto")
   dev.off()
   png(here("Plots", "Toys", "circle.png"))
   plot.graph.norm(g5, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-triangle.png"))
   plot.graph.norm(g6, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "circle-plus-long.png"))
   plot.graph.norm(g7, l = "circle")
   dev.off()
   png(here("Plots", "Toys", "clique.png"))
   plot.graph.norm(g8, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "kite.png"))
   plot.graph.norm(g9, l = "kk")
   dev.off()
   png(here("Plots", "Toys", "wheel.png"))
   plot.graph.norm(g10, l = "kk")
   dev.off()
```
